Information Retrieval - Submission Report \\Project N.14: Art For Sale

### 2023-12-11 docs/report/submission.tex
feat: submission report frontend
Signed-off-by: Jeferson Morales Mariciano <jeferson.morales.mariciano@gmail.com>

    \subsection{Frontend}\label{sec:frontend}
    Part of \textbf{Query and Retrieval Process},
    regarding \textbf{User Interaction}, in which the system supports the creation of a query and display results.\\
    The frontend is the main part of the application, where all the features are implemented.
    For the interface, it has been chosen a simple layout, consisting of only a search bar and a search button.
    Once the user performs the search, the aspect of the page changes, adding new components:

    \begin{figure}[H]
        \centering
        \caption{UI of the \textit{Art For Sale} project}
        \label{fig:carousel}
        \includegraphics[width=\textwidth, trim={7cm 0cm 7cm 2cm}, clip]{figures/ui.jpeg}
    \end{figure}

@@

    \subsubsection{User Interface}\label{sec:ui}

    Jacobs heuristics respected
    UI has been layed out following Jakob's 10 usability heuristics as much as possible:

    Emotional design: key in Apple, Google alike

    standard filtering system

    \subsubsection{Filtering}\label{sec:filtering}
    The filtering features is implemented frontend side:
    the filter string representation is checked in every documents, the ones which have it are still shown,
    otherwise it is hidden.
    If no filter is selected, then it simply shows all the results from the query.

>>>>

    \subsection{Frontend}\label{sec:frontend}
    Part of \textbf{Query and Retrieval Process},
    regarding \textbf{User Interaction}, in which the system supports the creation of a query and display results.\\
    The frontend is the main part of the application, where all the features are implemented.
    For the interface, it has been chosen a simple layout shown in Figure \ref{fig:ui},
    consisting of only a search bar and a search button.
    Once the user performs the search, the aspect of the page changes, adding new components:

    \begin{figure}[H]
        \centering
        \caption{UI of the \textit{Art For Sale} project}
        \label{fig:ui}
        \includegraphics[width=\textwidth, trim={7cm 0cm 7cm 2cm}, clip]{figures/ui.jpeg}
    \end{figure}

@@

    \subsubsection{User Interface}\label{sec:ui}
    UI has been layed out following Jakob's 10 usability heuristics as much as possible, particularly:
    aesthetic and minimalist design, visibility of system status and consistency and standards.\\
    Norman's Emotional Design guidelines have been followed to obtain a UI gradient effect and minimalism similar
    to what is the user experience in Apple products, so users will feel confortable using it.

    \subsubsection{Filtering}\label{sec:filtering}
    The filtering features is implemented frontend side.
    If no filter is selected, then it simply shows all the results from the query.
    Otherwise, it checks:
    \begin{itemize}
        \setlength\itemsep{0.1em}
        \item price value range: check if the document value is between the min and max inserted
        \item web sites: check if the document origin url contains the selected website(s)
        \item category: the UI allows only to select a category from the ones already present in the result of your query
    \end{itemize}
